### 2019-01-02 results.tex
Spectrum normalization units explained to resolve Reviewer 3 question 7 #35

\subsection{Neutron spectrum}
Figure~\ref{fig:spectrum} shows the normalized neutron flux spectrum for the 
full-core \gls{MSBR} model in the energy range from $10^{-8}$ to $10$ MeV. The 
neutron energy spectrum at equilibrium is harder than at startup due to 
plutonium and other strong absorbers accumulation in the core during reactor 
operation.  
\begin{figure}[ht!] % replace 't' with 'b'         to force it to 
  \centering
  \includegraphics[width=\textwidth]{spectrum.png} \caption{Neutron flux energy 
  spectrum normalized by unit lethargy for initial and equilibrium fuel salt 
  composition.}
  \label{fig:spectrum}
\end{figure}

@@

It is important to obtain the epithermal and thermal spectra to produce $^{233}$U from 
$^{232}$Th because the radiative capture cross section of thorium decreases monotonically 
from $10^{-10}$ MeV to $10^{-5}$ MeV. Hardening the spectrum tends to significantly 
increase resonance absorption in thorium and decrease absorptions in fissile and 
construction materials. 
\begin{figure}[ht!] % replace 't' with 'b' to force it to 
  \centering
  \includegraphics[width=\textwidth]{spectrum_zones.png} 
  \caption{Neutron flux energy spectrum in different core regions normalized by 
unit lethargy for the initial and equilibrium fuel salt composition.}
  \label{fig:spectrum_zones}
\end{figure}

>>>>

\subsection{Neutron spectrum}
Figure~\ref{fig:spectrum} shows the normalized neutron flux spectrum for the 
full-core \gls{MSBR} model in the energy range from $10^{-8}$ to $10$ MeV. The 
neutron energy spectrum at equilibrium is harder than at startup due to 
plutonium and other strong absorbers accumulation in the core during reactor 
operation.  
\begin{figure}[ht!] % replace 't' with 'b'         to force it to 
  \centering
  \includegraphics[width=\textwidth]{spectrum.png} \caption{Neutron flux energy 
  spectrum normalized by unit lethargy and area under the curve is normalized to 1 for initial and equilibrium fuel salt 
  composition.}
  \label{fig:spectrum}
\end{figure}

@@

It is important to obtain the epithermal and thermal spectra to produce $^{233}$U from 
$^{232}$Th because the radiative capture cross section of thorium decreases monotonically 
from $10^{-10}$ MeV to $10^{-5}$ MeV. Hardening the spectrum tends to significantly 
increase resonance absorption in thorium and decrease absorptions in fissile and 
construction materials. 
\begin{figure}[ht!] % replace 't' with 'b' to force it to 
  \centering
  \includegraphics[width=\textwidth]{spectrum_zones.png} 
  \caption{Neutron flux energy spectrum in different core regions normalized by 
unit lethargy and area under the curve is normalized to 1 for the initial and equilibrium fuel salt composition.}
  \label{fig:spectrum_zones}
\end{figure}
